---
title: "Pitch Presentation"
author: "Huibeom Kim"
date: "July 25, 2018"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

##Introduction
- I created a shiny application which show you a tree plot of Iris data, and tell you the Iris species depending on the value that you entered in the application.  
- You can do some manipulate in [this shiny app.](https://hbkim1293.shinyapps.io/ProjectApp/)
- This presentation is composed of
1. Shiny app's documentation
2. Code for the app

##Documentation  
  
- My application show tree plot depending on cp value which you can choose in slider. It is based on iris data.  
- You can also enter any value of Sepal.Length, Sepal.Width, Petal.Length, Petal.Width. Then my app will predict speices of iris based on values you choose.
```{r, message=FALSE, comment=""}
rbind(iris[1:2,], iris[51:52,], iris[101:102,])
```

##Code (Focus on reative command)
```{r, eval=FALSE, echo=TRUE}
#Each time you move the slider, cpvalue is recalculated and model is reconstructed. 
modFit <- reactive({
  cpInput <- input$cpslider
  rpart(Species ~., data = iris, control = rpart.control(cp = cpInput))
  })
#If you enter value on each textbox, app will predict species.
modPred <- reactive({
    SepalLengthPred <- as.numeric(input$SepalLength)
    SepalWidthPred <- as.numeric(input$SepalWidth)
    PetalLengthPred <- as.numeric(input$PetalLength)
    PetalWidthPred <- as.numeric(input$PetalWidth)
    predict(modFit(), newdata = data.frame(Sepal.Length = SepalLengthPred,
                            Sepal.Width = SepalWidthPred,
                            Petal.Length = PetalLengthPred,
                            Petal.Width = PetalWidthPred), type = "class")
  })
```

##Links 

- Play tha app here : https://hbkim1293.shinyapps.io/ProjectApp/
- Check full code here :   
https://github.com/hbkim1293/Course-Project
- Also check code for this presentation :  
https://github.com/hbkim1293/Course-Project/blob/master/myPresentation.Rmd